### 2020-11-25 README.Rmd
testing travis2

This repository contains the data and code for our paper:

@@

Our pre-print is online here:

@@

> Rodriguez-Machado, S., Rodríguez-Cabrera, T.M., and Chakrabarty, P. (2020), (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/sheilarm23/rrcompendium/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

>>>>

This repository contains the data and code for our future paper:

@@

which is still a work in progress...

Our pre-print will be online here:

@@

> Rodriguez-Machado, S. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/sheilarm23/rrcompendium/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. This way will take a few minutes to be ready but you will not need to install any packages on your computer.
